data_preparation

### 2024-03-24 src/data_prep/data_prep.Rmd
removed typos

Good. But before we can continue we have to do some 'eye-conemetrics' and show if there might be data pattern before we run our analysis. First, we look at how number of votes and rating behave for each genre.

@@

As you can see there is only a very small patern there. Typically, very few votes lead to all types of values, including extreme ones. However, as the number of votes seem to increase this extreme pattern decresaes slightly. This means that the number of votes continues to be relevant for our analysis and may even bias our results.

@@

As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthousiasm.

>>>>

Good. But before we can continue we have to do some 'eye-econemetrics' and show if there might be data pattern before we run our analysis. First, we look at how number of votes and rating behave for each genre.

@@

As you can see there is only a very small pattern there. Typically, very few votes lead to all types of values, including extreme ones. However, as the number of votes seem to increase this extreme pattern decreases slightly. This means that the number of votes continues to be relevant for our analysis and may even bias our results.

@@

As you can see, most of the genres appear to have some normal distribution going on. This is great! let's look at it with a qq plot to confirm our enthusiasm.
